---
title: "RWorksheet_Taghap#3"
author: "Vince Ryan Taghap"
date: "2022-10-23"
output: pdf_document
---



1. There is a built-in vector LETTERS contains the uppercase letters of the alphabet
and letters which contains the lowercase letters of the alphabet.

Based on the above vector LETTERS:

a. You need to produce a vector that contains the first 11 letters.
```{r vector1a}
    LET <- LETTERS[1:11]
    LET
```    
\hfill

b. Produce a vector that contains the odd numbered letters.
```{r vector1b}
    odd_LET <- LETTERS[1:26 %% 2 == 1]
    odd_LET
```  
\hfill

c. Produce a vector that contains the vowels
```{r vector1c}    
    vow_LET <- LETTERS[c(1,5,9,15,21)]
    vow_LET
```    
\hfill

Based on the above vector letters:
    
d. Produce a vector that contains the last 5 lowercase letters
```{r vector1d}    
    last_let <- letters[22:26]
    last_let
```    
\hfill

e. Produce a vector that contains letters between 15 to 24 letters in lowercase.
```{r vector1e}    
    let_between <- letters[16:23]
    let_between
```
\hfill
    
2. Create a vector with the average temperatures in April for Tuguegarao City, Manila,
Iloilo City, Tacloban, Samal Island, and Davao City. The average temperatures in
Celcius are 42, 39, 34, 34, 30, and 27 degrees.
    
a. What is the R code and its result for creating a character vector for the city/town of
    Tuguegarao City, Manila, Iloilo City, Tacloban, Samal Island, and Davao City? Name the
    object as city. The names should follow the same order as in the instruction.
```{r vector1z}    
    
    city <- c("Tuguegarao City", "Manila", "Iloilo City", "Tacloban", "Samal Island", "Davao City")
    city
```    
\hfill

b. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.
    Name the object as temp. Write the R code and its output. Numbers should also follow what
    is in the instruction.
```{r vector1f}    
    temp <- c(42, 39, 34, 34, 30, 27)
    temp
```  
\hfill

c. Associate the temperature temp with the city by using names() function. What is
    the R code and its result?   
```{r vector1g}    
    names(temp) <- city
    temp
```    
e. From the answer in d, what is the content of index 5 and index 6? What is its R code?
```{r vector1h}    
    five_six <- temp[5:6]
    five_six
```    
\hfill

   Using Matrices   
    
2. Create a matrix of one to eight and eleven to fourteen with four columns and three
    rows.
    
a. What will be the R code for the #2 question and its result?
```{r vector1i}    
    table <- matrix(c(1:8, 11:14), nrow = 3, ncol =4)
    table
```    
\hfill
    
b. Multiply the matrix by two. What is its R code and its result?
```{r vector1j}    
    table <- matrix(c(1:8, 11:14), nrow = 3, ncol =4)
    table
    
    table2 <- table * 2
    table2
```
\hfill

c. What is the content of row 2? What is its R code?
```{r vector1k}    
    table <- matrix(c(1:8, 11:14), nrow = 3, ncol =4)
    table
    
    row2 <- table[2,1:4]
    row2
```  
\hfill

d. What will be the R code if you want to display the column 3 and column 4 in row 1
    and row 2? What is its output?
```{r vector1l}    
    table <- matrix(c(1:8, 11:14), nrow = 3, ncol =4)
    table
    
    col3_4 <- c(table[1,3:4], table[2,3:4])
    col3_4
```    
\hfill

e. What is the R code is you want to display only the columns in 2 and 3, row 3? What
    is its output?
```{r vector1m}    
    table <- matrix(c(1:8, 11:14), nrow = 3, ncol =4)
    table
    
    col2_3 <- table[3,2:3]
    col2_3
```
\hfill

f. What is the R code is you want to display only the columns 4? What is its output? 
```{r vector1n}
    table <- matrix(c(1:8, 11:14), nrow = 3, ncol =4)
    table
    
    col4 <- table[1:3,4]
    col4
```    
\hfill

g. Name the rows as isa, dalawa, tatlo and columns as uno, dos, tres, quatro
    for the matrix that was created in b.‘. What is its R code and corresponding output?
```{r vector1o}    
    table <- matrix(c(1:8, 11:14), nrow = 3, ncol =4)
    table
    
    dimnames(table) <- list(c("isa", "dalawa", "tatlo"), c("uno", "dos", "tres", "quatro"))
    table
```    
\hfill

h. From the original matrix you have created in a, reshape the matrix by assigning a
    new dimension with dim(). New dimensions should have 2 columns and 6 rows. What will
    be the R code and its output?
```{r vector1p}    
    table <- matrix(c(1:8, 11:14), nrow = 3, ncol =4)
    table
    
    dim(table) <- c(6,2)
    table
```
\hfill

    #Using Arrays    
    
3. An array contains 1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1
```{r vector1q}    
    nums <- c(1, 2, 4, 6, 7, 8, 9, 0, 3, 4, 5, 1)
    nums
```    
\hfill

a. Create an array for the above numeric values. Each values will be repeated twice
    What will be the R code if you are to create a three-dimensional array with 4 columns and 2
    rows. What will be its output?
```{r vector1r}    
    arr <- array(rep(nums, 2), dim = c(2,4,3))
    arr
```    
\hfill

b. How many dimensions do your array have?
    
    #The array has a three(3) dimensions
    
c. Name the rows as lowercase letters and columns as uppercase letters starting from
    the A. The array names should be “1st-Dimensional Array”, “2nd-Dimentional Array”, and
    “3rd-Dimensional Array”. What will be the R codes and its output?
```{r vector1s}    
    dimnames(arr) <- list(letters[1:2], LETTERS[1:4], c("1st-Dimensional Array", "2nd-Dimensional Array", "3rd-Dimensional Array"))
    arr
```    

