---
title: "RWorksheet-3b"
author: "Vince Ryan Taghap"
date: "2022-11-22"
output: pdf_document
---


\hfill\break
1.Create a data frame using the table below.

a. Write the codes.
```{r, vector = TRUE}
table <- data.frame(
                    Respondents = c(1:20),
                    Sex = c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2),
                    Father= c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1),
                    Persons = c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6),
                    Siblings = c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2),
                    Houses = c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)

                    )


names(table) <- list("Respondents","Sex","Fathers occupation","Persons at Home",
                      "Siblings at School", "Types of Houses")

table
```
\hfill
b.Describe the data. Get the structure or the summary of the data
```{r, vector = TRUE}
sum_table <- summary(table)
sum_table
```
\hfill
c. Is the mean number of siblings attending is 5?
```{r, vector = TRUE}
table_mean <-mean(table$Siblings)
table_mean
#NO
```
\hfill
d.Extract the 1st two rows and then all the columns using the subsetting 
functions.

Write the codes and its output.

```{r, vector = TRUE}
extract_1 <- subset(table[1:2,1:6])
extract_1
```
\hfill
e Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its
result.
```{r, vector = TRUE}
extract_2 <- subset(table[c(3,5), c(2,4)])
extract_2
```
\hfill
f. Select the variable types of houses then store the vector that results as 
types_houses.

Write the codes.
```{r, vector = TRUE}
types_houses <- table$"Types of Houses"
types_houses
```
\hfill
g.Select only all Males respondent that their father occupation was farmer.Write
the codes and its output.

```{r, vector = TRUE}
male_subset <- subset(table, Sex == '1', 'Fathers Occupation'== '1') 
male_subset

#There is no result because in the data frame there is no male respondents that 
#their father occupation is farmer.
```
\hfill
h. Select only all females respondent that have greater than or equal to 5
number of siblings attending school. Write the codes and its outputs.
```{r, vector = TRUE}
female_subset <- subset(table[c(1:20), c(2,5)])
female_subset

female <- female_subset[table$`Siblings at School` >= '5',]
female
```
\hfill\break
2. Write a R program to create an empty data frame. Using the following codes:
```{r, vector = TRUE}
  df = data.frame(Ints=integer(),
                  Doubles=double(), Characters=character(),
                  Logicals=logical(),
                  Factors=factor(),
                  stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```
\hfill
a. Describe the results.
```{r, vector = TRUE}
#The data frame is an empty data frame. It has zero columns, 5 rows and zero 
#level.
```
\hfill\break
3. Interpret the graph.

Figure 1: Sentiments of Tweets per day - Donald Trump
```{r, vector = TRUE}
#The table shows that there are more negative comments than neutral and positive comments from 
#July 14 to July 21 about Donald Trump.
```








