---
title: "Worksheet 7a"
author: "Vince Ryan Taghap"
date: "2022-12-13"
output: pdf_document
---

\hfill\break
1. Create a data frame for the table below 
```{r,vector = TRUE}
  scores_df <- data.frame(
    Student = seq(1:10),
    Pre_test = c(55,54,47,57,51,61,57,54,63,58),
    Post_test = c(61,60,56,63,56,63,59,56,62,61)
                )
  names(scores_df) <- list("Student", "Pre-test", "Post-test")
  
  scores_df
```

\hfill\break
a. Compute the descriptive statistics using different packages 
(Hmisc and pastecs).
\hfill\break
Write the codes and its result.

```{r,vector = TRUE}
library(Hmisc)
library(pastecs)

  describe(scores_df)
  stat.desc(scores_df)
```

\hfill\break
2. The Department of Agriculture was studying the effects of several levels 
of a fertilizer on the growth of a plant. For some analyses, it might be
useful to convert the fertilizer levels to an ordered factor.

```{r,vector = TRUE}
  Dept_of_Agri <- c(10,10,10,20,20,50,10,20,10,50,20,50,20,10)
  Dept_of_Agri
```
\hfill\break
a. Write the codes and describe the result.
```{r,vector = TRUE}
ord <- sort(Dept_of_Agri, decreasing = FALSE)
ord
```
\hfill\break
3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study
the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” ,
“l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense

```{r,vector = TRUE}
  Subjects <- c("l","n","n","i","l","l","n","n","i","l")
  Subjects
```
\hfill\break
a. What is the best way to represent this in R?

```{r,vector = TRUE}
# Answer: Dataframe 

  subs <- data.frame(Subjects)
  subs 
```
\hfill\break
4.Sample of 30 tax accountants from all the states and territories of 
Australia and their individual state of origin is specified by a character 
vector of state mnemonics
as:

```{r,vector = TRUE}
  state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
  state  
```
\hfill\break
a. Apply the factor function and factor level. Describe the results.

```{r,vector = TRUE}
  ff <- factor(state)
  ff
```
\hfill\break
5. From #4 - continuation:
\hfill\break
• Suppose we have the incomes of the same tax accountants in another vector 

```{r,vector = TRUE}
  incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
  incomes
```
\hfill\break
a. Calculate the sample mean income for each state we can now use the special
function tapply():

```{r,vector = TRUE}
  cal <- tapply(state, incomes, mean)
  cal
```
\hfill\break
b. Copy the results and interpret.

```{r,vector = TRUE}
# 40 41 42 43 46 48 49 51 52 54 56 58 59 60 61 62 64 65 69 70 
#NA NA NA NA NA NA NA NA NA NA NA NA NA NA NA NA NA NA NA NA
```
\hfill\break
6.Calculate the standard errors of the state income means (refer again to 
number 3)

```{r,vector = TRUE}
  stdError <- function(x) sqrt(var(x)/length(x))
  stdError(subs)
  incster <- tapply(incomes, state, stdError)
```
\hfill\break
a. What is the standard error? Write the codes.
```{r,vector = TRUE}
  # Answer: NA
```
\hfill\break
b. Interpret the result.
```{r,vector = TRUE}
  #Because some variables are character types, the result is unavailable. 
  #Therefore, the standard error cannot be determined.
```
\hfill\break
7. Use the titanic dataset.
```{r,vector = TRUE}
  data("Titanic")

  titanic_df<- data.frame(Titanic)
```
\hfill\break
a. subset the titatic dataset of those who survived and not survived. Show the
codes and its result.

```{r,vector = TRUE}
  hsbst <- subset(titanic_df, select = "Survived")
  hsbst
```
\hfill\break
8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically as 
Dr. Wolberg reports his clinical cases. The database therefore reflects this
chronological grouping of the data. You can create this dataset in Microsoft Excel.
\hfill\break
a. describe what is the dataset all about.
```{r,vector = TRUE}
  #The dataset is all about Breast Cancer.
```
\hfill\break
b. Import the data from MS Excel. Copy the codes.
```{r,vector = TRUE}
library("readxl")
  data <- read_excel("C:/Users/TAGHAP/Desktop/Master Vinsoy/VINCE RYAN TAGHAP/BSIT 2A (1st sem)/DATA SCIENCE/worksheet 7a/Breast_Cancer.xlsx")
  
  data
```
\hfill\break
c. Compute the descriptive statistics using different packages. Find the values of:
\hfill\break
c.1 Standard error of the mean for clump thickness.

```{r,vector = TRUE}
  clump <- length(data$`CL. thickness`)
  clump1 <- sd(data$`CL. thickness`)
  clump2 <- clump1/sqrt(data$`CL. thickness`)
  clump2
```
\hfill\break
c.2 Coefficient of variability for Marginal Adhesion.
```{r,vector = TRUE}
  cov <- sd(data$`Marg. Adhesion`) / mean(data$`Marg. Adhesion`)* 100
  cov
```
\hfill\break
c.3 Number of null values of Bare Nuclei.
```{r,vector = TRUE}
  nv <- subset(data,`Bare. Nuclei` == "NA")
  nv
```
\hfill\break
c.4 Mean and standard deviation for Bland Chromatin
```{r,vector = TRUE}
  mean(data$`Bl. Cromatin`)
  sd(data$`Bl. Cromatin`)
```
\hfill\break
c.5 Confidence interval of the mean for Uniformity of Cell Shape
\hfill\break
Calculate the mean
```{r,vector = TRUE}
  calm <- mean(data$`Cell Shape`)
  calm
```
\hfill\break
Calculate the standard error of the mean

```{r,vector = TRUE}
  se <- length(data$`Cell Shape`)
  se1 <- sd(data$`Cell Shape`)
  ser <- se1/sqrt(se)
  ser
```
\hfill\break
Find the t-score that corresponds to the confidence level

```{r,vector = TRUE}
  tscore = 0.05
  tse = se - 1
  cl = qt(p = tscore/ 2, df = tse,lower.tail = F)
  cl
```
\hfill\break
Constructing the confidence interval
```{r,vector = TRUE}
  ci <- cl * ser
  
```
\hfill\break
Lower

```{r,vector = TRUE}
  lower <- calm - ci
  
```
\hfill\break
Upper

```{r,vector = TRUE}
  upp <- calm + ci

  grpLU <- c(lower,upp)
```
\hfill\break
d. How many attributes?
```{r,vector = TRUE}
  att <- attributes(data)
  att
```
\hfill\break
e. Find the percentage of respondents who are malignant. Interpret the results.
```{r,vector = TRUE}
  perres <- subset(data, Class == "malignant")
  perres
```
\hfill\break
There 18 respondents who are malignant dnd there are total of 49 respondents.
\hfill\break
Getting the percentage

```{r,vector = TRUE}
  getper <- 17  / 49 * 100
  getper
```
\hfill\break
9. Export the data abalone to the Microsoft excel file. Copy the codes.
```{r,vector = TRUE}

library("AppliedPredictiveModeling")
  data("abalone")
  View(abalone)
  head(abalone)
  summary(abalone)
```
\hfill\break
Exporting the data abalone to the Microsoft excel file
```{r,vector = TRUE}
  library(xlsx)
  write.xlsx(abalone, "abalone.xlsx")
```
