---
title: "RWorksheet-4"
author: "Vince Ryan Taghap"
date: "2022-11-22"
output: pdf_document
---
\hfill\break

1.The table below shows the data about shoe size and height. 
Create a data frame...

```{r,vector = TRUE}
shoe_table <- data.frame(
          shoesize = c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.0,
                        10.5,13.0,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,8.5,10.5,
                        11.0,9.0,13.0),
          height = c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,
                      67.0,71.0,71.0,77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,
                      73.0,69.0,72.0,70.0,69.0,70.0), 
         gender = c("F","F","F","F","M","F","F","F","M","F","M","F","M","M","M",
                    "M","F","F","M","F","F","M","M","F","M","M","M","M") 
                        )

names(shoe_table) <- list("Shoe size", "Height", "Gender")
shoe_table
```
\hfill\break
a. Describe the data. 
```{r,vector = TRUE}
#The data shows the different shoe size among male and female in different 
#heights.
```
\hfill\break
b. Find the mean of shoe size and height of the respondents.
Copy the codes and results.
```{r,vector = TRUE}
#Shoe Mean
shoe_mean <- mean(shoe_table$`Shoe size`)
shoe_mean



#Height Mean
height_mean <- mean(shoe_table$Height)
height_mean
```
\hfill\break
c. Is there a relationship between shoe size and height?Why? 
```{r,vector = TRUE}
#Yes, there is a relationship between shoe size and height, I can imagine that 
#your shoe size is large, you are also tall. The taller the height, the bigger
#the shoe size.
```
\hfill\break
Using factor() 
```{r,vector = TRUE}
#examples
Gender <- c("M","F","F","M")
factor_Gender <- factor(Gender)
factor_Gender
```
\hfill\break
2. Construct character vector months to a factor with factor() and assign the 
result to factor_months_vector. Print out factor_months_vector and assert that 
R prints out the factor levels below the actual values.

```{r,vector = TRUE}
vector_months <- c("March","April","January","November","January","September",
                   "October","September","November","August","January",
                   "November","November","February","May","August","July",
                   "December","August","August","September","November",
                   "February","April")

vector_months

factor_months_vector <- factor(vector_months)
factor_months_vector 
```
\hfill\break
3.Then check the summary() of the months_vector and factor_months_vector. 
Interpret the results of both vectors.Are they both equally useful in this case? 

```{r,vector = TRUE}
sum_vec <- summary(vector_months)
sum_vec

sum_fac <- summary(factor_months_vector)
sum_fac
```
\hfill\break
4. Create a vector and factor for the table below.
```{r,vector = TRUE}
factor_data <- c("East" = '1', "West" = '4', "North" = '3')
factor_data

new_order_data <- factor(factor_data,levels = c("East" = '1',  "West" = '4',  
                                                "North" = '3'))
print(new_order_data)
```
\hfill\break
5. Enter the data below in Excel with file name = import_march.csv
\hfill\break
a. Import the excel file into the Environment Pane using read.table() function.
Write the code.

```{r,vector = TRUE}
import <- read.table("import_march.csv", header = T, sep = ",")
import
```
\hfill\break
b. View the dataset. Write the code and its result
```{r,vector = TRUE}
View(import)
```

