---
title: 'RWorksheet #6'
author: "Vince Ryan Taghap"
date: "2022-11-25"
output: pdf_document
---

```{r,vector = TRUE}
library(dplyr)
library(ggplot2)
```
\hfill\break
```{r,vector = TRUE}
data(mpg)

mpg_df <- as.data.frame(mpg)
mpg_df
```
\hfill\break
1. How many columns are in mpg dataset? How about the number of rows? 
Show the codes and its result.

```{r,vector = TRUE}
mpg_data <- glimpse(mpg_df)


#There are 234 rows and 11 columns.
```
\hfill\break
2. Which manufacturer has the most models in this data set? Which model has the most
variations?

```{r,vector = TRUE}
#Dodge, it has 37 models. While the most variations for model are the caravan2wd
```
\hfill\break
```{r,vector = TRUE}
man_count <- mpg_data %>% group_by(manufacturer,model) %>% count()
colnames(man_count) <- list("Manufacturer","Model","Counts")

man_count
```
\hfill\break
a. Group the manufacturers and find the unique models. Copy the codes and result.

```{r,vector = TRUE}
grp_unique <- mpg_data %>% group_by(manufacturer, model) %>% distinct() %>% count()
colnames(grp_unique) <- list("Manufacturer", "Model","Counts")

grp_unique
```
\hfill\break
b. Graph the result by using plot() and ggplot(). Write the codes and its result

```{r,vector = TRUE}
#Plot
plot(man_count)

#GGPlot
ggplot(man_count, aes(Manufacturer, Model)) + geom_point()
```
\hfill\break
3. Same dataset will be used. You are going to show the relationship of the model and
the manufacturer.
\hfill\break
a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r,vector = TRUE}
#It shows in the point graph what is the manufacturer of the said model. It helps 
#the user to analyze the data easily and informative.
ggplot(mpg_df, aes(model, manufacturer)) + geom_point()
```
\hfill\break
b. For you, is it useful? If not, how could you modify the data to make it more
informative?

```{r,vector = TRUE}
#The data is very useful. It is simple and easy to analyze.
```
\hfill\break
4. Using the pipe (%>%), group the model and get the number of cars per model. 
Show codes and its result.
```{r,vector = TRUE}
grp_data <- mpg_data %>% group_by(model) %>% count()
colnames(grp_data) <- c("Model","Counts")

grp_data
```
\hfill\break
a. Plot using the geom_bar() + coord_flip() just like what is shown below. 
Show codes and its result.
```{r,vector = TRUE}
qplot(model,data = mpg_df,
      main = "Number of Cars per Model",
      xlab = "Model",
      ylab = "Number of Cars", geom = "bar", fill = manufacturer) + coord_flip()
```
\hfill\break
b. Use only the top 20 observations. Show code and results.

```{r,vector = TRUE}
top_20 <- grp_data[1:20,] %>% top_n(2)
colnames(top_20) <- c("Model","Counts")

top_20
                        
ggplot(top_20,aes(x = Model, y = Counts)) +
  geom_bar(stat = "Identity") +coord_flip()
```
\hfill\break
5. Plot the relationship between cyl - number of cylinders and displ - engine 
displacement using geom_point with aesthetic colour = engine displacement. Title should be
“Relationship between No. of Cylinders and Engine Displacement”.
\hfill\break
a. Show the codes and its result

```{r,vector = TRUE}
ggplot(data = mpg_data , mapping = aes(x = displ, y = cyl, main = "Relationship
between No. of Cylinders and Engine Displacement")) +
  geom_point(mapping=aes(colour = "engine displacement"))
```
\hfill\break
b. How would you describe its relationship?

```{r,vector = TRUE}
#The scatter plot shows that the cyl is in y axis and the displ are in the x axis 
#to easily distinguish the clustered data, which indicate the engine displacement.
```
\hfill\break
6. Get the total number of observations for drv - type of drive train (f = front-wheel drive,
r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.).
Plot using the geom_tile() where the number of observations for class be used as a
fill for aesthetics.
\hfill\break
a. Show the codes and its result for the narrative in #6
```{r,vector = TRUE}
ggplot(data = mpg_data, mapping = aes(x = drv, y = class)) +
  geom_tile(aes(fill=class))
```
\hfill\break
b. Interpret the result.

```{r,vector = TRUE}
#By mapping a geometric tile, it graph the data in a tile graph that was shown in
#different colors.The data shows the drv of each class.
```
\hfill\break
7. Discuss the difference between these codes. Its outputs for each are shown below.
```{r,vector = TRUE}
# Code #1
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

\hfill\break
```{r,vector = TRUE}
#+ Code #2
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```
\hfill\break
```{r,vector = TRUE}
#The difference between these two codes are they have the same color value which is blue 
#but in the output in the code #1 it has a color red dots while the code #2 has 
#a color blue dots. It is because the value of the color in code #1 is belong in
#the aes function, thats why the value of the color don't matter. Unlike in the code #2
#whereas the value of the color are outside is the value of function aes.
```
\hfill\break
8. Try to run the command ?mpg. What is the result of this command?
```{r,vector = TRUE}
?mpg
#The result of this command is it shows the description of the data set mpg.
#In other terms the "?" command is also known as help.
```
\hfill\break
a. Which variables from mpg dataset are categorical?

```{r,vector = TRUE}
#The variables that are categoral in mpg dataset are the manufacturer, model, 
#trans, drv, fl, class are the categorical variables from the data-set of mpg.
```
\hfill\break
b. Which are continuous variables?

```{r,vector = TRUE}
#The continuous variable of the mpg data-set are the dsipl, year,
#cyl, cty, and hwy.
```
\hfill\break
c. Plot the relationship between displ (engine displacement) and hwy(highway miles
per gallon). Mapped it with a continuous variable you have identified in #5-b. 
What is its result? Why it produced such output?

```{r,vector = TRUE}
ggplot(mpg, aes(x = cty, y = hwy, colour = displ)) + geom_point()
#The data that have been graph shows that they are in the positive rate using the 
#displ for hwy and cty scattered plot. The data tracks the cty by placing cty at 
#color that having a variations of color blue.
```
\hfill\break
9. Plot the relationship between displ (engine displacement) and hwy(highway miles
per gallon) using geom_point(). Add a trend line over the existing plot using
geom_smooth() with se = FALSE. Default method is “loess”.

```{r,vector = TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE)
```
\hfill\break
10. Using the relationship of displ and hwy, add a trend line over existing plot.
Set the se = FALSE to remove the confidence interval and method = lm to check 
for linear modeling.
```{r,vector = TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)
```
