---
title: 'Project #2'
author: "Vince Ryan Taghap"
date: "2022-12-11"
output:
  html_document: default
  pdf_document: default
---

```{r,vector = TRUE}
library(twitteR)
library(dplyr)
library(rtweet)
library(ggplot2)
library(tidytext)
library(RColorBrewer)
library(tm)
library(plotly)
```
\hfill\break
```{r,vector = TRUE}
CONSUMER_SECRET <- "PvNTAZrNQNUPf655uhQGDvqnBhEkOtdnCUChsPooSBWrMeCdj6"
CONSUMER_KEY <- "0eKM7ywAbJIBhoc6qUtPGZ2gc"
ACCESS_SECRET <- "qSvpFsynx6zadfrSvrTaihnqm4jfZ4XNEI6F6LwmWJ2B7"
ACCESS_TOKEN <- "1594992291864727553-wz6TgceS7HWYmZ7Tvn05kMNFAOBkaw"
```
\hfill\break
```{r,vector = TRUE}
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```
\hfill\break
Extract 10000 tweets from Twitter using twitteR package including retweets

```{r,vector = TRUE}
NBAtweets <- searchTwitter("NBA",
                      n=10000,
                      since = "2022-12-05",
                      until = "2022-12-11",
                      lang = "en",
                      retryOnRateLimit = 120
                      )
```

\hfill\break
Convert into Data Frame
\hfill\break
```{r,vector = TRUE}
NBAdf <- twListToDF(NBAtweets)
head(NBAdf$text)[1:5]
```
\hfill\break
Saving and loading the Data Frame
\hfill\break
```{r,vector = TRUE}
save(NBAdf,file = "NBAdf.Rdata")
load(file = "NBAdf.Rdata")
```
\hfill\break
----Original Tweets-----
\hfill\break

Subsetting original tweets
\hfill\break
```{r,vector = TRUE}
tweetsNBA <- NBAdf %>%
  select(screenName,text,created,isRetweet) %>% filter(isRetweet == FALSE)
```

\hfill\break
Saving and loading Original Tweets
```{r,vector = TRUE}
save(tweetsNBA,file = "Original_Tweetsdf.Rdata")
load(file = "Original_Tweetsdf.Rdata")
```

\hfill\break
Grouping the data created
\hfill\break
```{r,vector = TRUE}
tweetsNBA %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

data1 <- tweetsNBA %>%  mutate(Created_At_Round = created %>% round(units = 'hours')
                               %>% as.POSIXct())

mn <- tweetsNBA %>% pull(created) %>% min()
mn 
mx <- tweetsNBA %>% pull(created) %>% max()
mx
```
\hfill\break
Plot on original tweets by time.
\hfill\break
```{r,vector = TRUE}
Orig_plot <- ggplot(data1, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of Tweets") + 
  scale_fill_gradient(low = "midnightblue", high = "aquamarine4")

Orig_plot %>% ggplotly()
```
\hfill\break
================================================================================
\hfill\break

----ReTweets----
\hfill\break

Subsetting retweets
\hfill\break
```{r,vector = TRUE}
NBA_retweets <- NBAdf %>%
  select(screenName,text,created, isRetweet) %>% filter(isRetweet == TRUE)
```

Saving and loading ReTweets
```{r,vector = TRUE}
save(NBA_retweets,file = "ReTweetsdf.Rdata")
load(file = "ReTweetsdf.Rdata")
```

\hfill\break
Grouping the data created
\hfill\break
```{r,vector = TRUE}
NBA_retweets %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

data2 <- NBA_retweets %>%  mutate(Created_At_Round = created %>% round(units = 'hours') %>% as.POSIXct())

mn <- NBA_retweets %>% pull(created) %>% min()
mn 
mx <- NBA_retweets %>% pull(created) %>% max()
mx
```
\hfill\break
Plot on reTweets by time
\hfill\break
```{r,vector = TRUE}
reTweet_plot <- ggplot(data2, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of ReTweets") + 
  scale_fill_gradient(low = "midnightblue", high = "aquamarine4")

reTweet_plot %>% ggplotly()
```